\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
fix path to image
break at 80

\begin{wrapfigure}{r}{0.7\linewidth}
\caption{Filtering steps.}\label{wrap-fig:1}
\includegraphics[width=\linewidth]{code/code/fig_filtering.png}
\end{wrapfigure}

@@

\textcolor{red}{Then we apply on the entire signal a non-linear filter base on the current activity of the systems in order to favor the association measure inversely proportional to the number of neurons firing together:$ X_{t,w}^i  = (X_{t,d}^i + 1 )^{1 + \frac{1}{\sum_{j} X_{t,d}^j}} $. When too much neurons are firing together, i.e. a network burst, it is almost impossible to retrieve direct relationships: all neurons seem to be directly connected to each other. By favoring the association measure when the activity is low, we expect to retrieve a pair of neurons that are really directly connected together. 
}

@@

Since all neurons are assumed to be connected to at least one neuron,
we thus have by definition $X_i \not\perp X_j$. However,  two random
variables $A$ and $B$ might be dependent taken alone ($A \not\perp B$), but not
once we observe the set  $C$ of all other variables ($A \perp B | C$).
The conditioning over all other random variables $X^{-i,j}$ is thus necessary
to avoid predicting an edge when two neurons are not directly connected.

>>>>

\begin{wrapfigure}{r}{0.7\linewidth}
\caption{Filtering steps.}\label{wrap-fig:1}
\includegraphics[width=\linewidth]{images/fig_filtering_recut.png}
\end{wrapfigure}

@@

\textcolor{red}{Then we apply on the entire signal a non-linear filter base on the 
current activity of the systems in order to favor the association measure inversely 
proportional to the number of neurons firing together:
$ X_{t,w}^i  = (X_{t,d}^i + 1 )^{1 + \frac{1}{\sum_{j} X_{t,d}^j}} $. 
When too much neurons are firing together, i.e. a network burst, it is almost 
impossible to retrieve direct relationships: all neurons seem to be directly 
connected to each other. By favoring the association measure when the activity is low, 
we expect to retrieve a pair of neurons that are really directly connected together. 
}

@@

Since all neurons are assumed to be connected to at least one neuron,
we thus have by definition $X_i \not\perp X_j$ \textcolor{red}{AS: Je ne suis pas sûr de comprendre.}. However,  two random
variables $A$ and $B$ might be dependent taken alone ($A \not\perp B$), but not
once we observe the set  $C$ of all other variables ($A \perp B | C$).
The conditioning over all other random variables $X^{-i,j}$ is thus necessary
to avoid predicting an edge when two neurons are not directly connected.
